Secure Composition \\ of Robust and Optimising Compilers

### 2024-05-24 csf2/main.tex
use ghostarrow in spec

  %
  \typerule{$e-\ird{ifz}-\ird{true}-\text{spec}$}{
    \ird{\cfstate[']}.\ird{\operatorname{win}} = \omega
  }{
    \pstepto{\rtt{\ird{\cfstate;\sandboxtag;0;\memstate}}{\ird{\lifz{0^{\securitytag}}{\expr[_1]}{\expr[_2]}}}}{\begin{array}{c}\rtt{\ird{\cfstate['];\sandboxtag;0;\memstate}}{\ird{\expr[_1]}}\\\rtt{\ird{\cfstate;\sandboxtag;0;\memstate}}{\ird{\expr[_2]}}\end{array}}{\ird{\ev{Branch}\ 0;\sandboxtag;\securitytag}\cdot\ird{\ev{Spec};\sandboxtag;\securitytag}}
  }{e-ifz-true-spec}
  %
  \typerule{$e-\ird{spec}-\text{eat}$}{
    \ird{\cfstate}.\ird{\operatorname{win}} > 0 &
    \pstepto{\rtt{\ird{\cfstate;\sandboxtag;0;\memstate}}{\ird{\expr}}}{\rtt{\ird{\cfstate['];\sandboxtag;0;\memstate}}{\ird{\expr[']}}}{\ird{\event}} &
    \ird{\cfstate['']}.\ird{\operatorname{win}} = \ird{\cfstate[']}.\ird{\operatorname{win}}-1
  }{
    \pstepto{\begin{array}{c}\rtt{\ird{\cfstate;\sandboxtag;0;\memstate}}{\ird{\expr}}\\\ird{r}\end{array}}{\begin{array}{c}\rtt{\ird{\cfstate[''];\sandboxtag;0;\memstate}}{\ird{\expr[']}}\\\ird{r}\end{array}}{\ird{\event}}
  }{e-spec-eat}
  % 
  \typerule{$e-\ird{spec}-\text{eaten}$}{
    \ird{r}.\ird{\cfstate}.\ird{\operatorname{win}} = 0
  }{
    \pstepto{\begin{array}{c}\ird{r}\\\ird{r'}\end{array}}{\ird{r'}}{\ird{Rlb}}
  }{e-spec-eaten}
  %
  \typerule{$e-\ird{spec}-\text{barrier}$}{
    \ird{r'}.\ird{\cfstate} = \ird{r}.\ird{\cfstate}[.\ird{\operatorname{win}} = 0]
  }{
    \pstepto{\begin{array}{c}\ird{r}\\\ird{r''}\end{array}}{\begin{array}{c}\ird{r'}\\\ird{r''}\end{array}}{\ird{Barrier}}
  }{e-spec-barrier}
\end{center}

>>>>

  %
  \typerule{$e-\ird{ifz}-\ird{true}-\text{spec}$}{
    \ird{\cfstate[']}.\ird{\operatorname{win}} = \omega
  }{
    \pstepto{\rtt{\ird{\cfstate;\sandboxtag;0;\memstate}}{\ird{\lifz{0^{\securitytag}}{\expr[_1]}{\expr[_2]}}}}{\begin{array}{c}\rtt{\ird{\cfstate['];\sandboxtag;0;\memstate}}{\ird{\expr[_1]}}\\\rtt{\ird{\cfstate;\sandboxtag;0;\memstate}}{\ird{\expr[_2]}}\end{array}}{\ird{\ev{Branch}\ 0;\sandboxtag;\securitytag}\cdot\ird{\ev{Spec};\sandboxtag;\securitytag}}
  }{e-ifz-true-spec}
  %
  \typerule{$e-\ird{spec}-\text{eat}$}{
    \ird{\cfstate}.\ird{\operatorname{win}} > 0 &
    \pstepto{\rtt{\ird{\cfstate;\sandboxtag;0;\memstate}}{\ird{\expr}}}{\rtt{\ird{\cfstate['];\sandboxtag;0;\memstate}}{\ird{\expr[']}}}{\ird{\event}} &
    \ird{\cfstate['']}.\ird{\operatorname{win}} = \ird{\cfstate[']}.\ird{\operatorname{win}}-1
  }{
    \ghoststepto{\begin{array}{c}\rtt{\ird{\cfstate;\sandboxtag;0;\memstate}}{\ird{\expr}}\\\ird{r}\end{array}}{\begin{array}{c}\rtt{\ird{\cfstate[''];\sandboxtag;0;\memstate}}{\ird{\expr[']}}\\\ird{r}\end{array}}{\ird{\event}}
  }{e-spec-eat}
  % 
  \typerule{$e-\ird{spec}-\text{eaten}$}{
    \ird{r}.\ird{\cfstate}.\ird{\operatorname{win}} = 0
  }{
    \ghoststepto{\begin{array}{c}\ird{r}\\\ird{r'}\end{array}}{\ird{r'}}{\ird{Rlb}}
  }{e-spec-eaten}
  %
  \typerule{$e-\ird{spec}-\text{barrier}$}{
    \ird{r'}.\ird{\cfstate} = \ird{r}.\ird{\cfstate}[.\ird{\operatorname{win}} = 0]
  }{
    \ghoststepto{\begin{array}{c}\ird{r}\\\ird{r''}\end{array}}{\begin{array}{c}\ird{r'}\\\ird{r''}\end{array}}{\ird{Barrier}}
  }{e-spec-barrier}
\end{center}
